---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# sharefs

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/orgadish/sharefs/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/orgadish/sharefs/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/sharefs)](https://cran.r-project.org/package=sharefs)
[![CRAN downloads](https://cranlogs.r-pkg.org/badges/grand-total/sharefs)](https://cran.r-project.org/package=sharefs)
<!-- badges: end -->

sharefs lists and copies files with minimal network calls -- useful when
reading from a network share (a mapped drive, a UNC path, an SMB/CIFS
mount), where listing a directory and `stat()`-ing each file separately
normally costs one network round trip per file. `sfs_dir_info()` uses a
single `Get-ChildItem` call instead, and `sfs_stage_local()` copies files
to local disk (via `sfs_robocopy()`) before you read them.

sharefs is Windows-only (`OS_type: windows`). `sfs_dir_info()` requires
PowerShell (see `sfs_powershell_available()`) and errors if it isn't
available.

## Installation

```{r, eval = FALSE}
if (!requireNamespace("remotes")) install.packages("remotes")
remotes::install_github("orgadish/sharefs")
```

## Usage

```{r example}
library(sharefs)

# A UNC path or mapped network drive in practice; a local temp
# directory here so this example actually runs.
network_location <- tempfile()
dir.create(network_location)
write.csv(data.frame(x = 1:2), file.path(network_location, "a.csv"), row.names = FALSE)
write.csv(data.frame(x = 3:4), file.path(network_location, "b.csv"), row.names = FALSE)

sfs_dir_info(network_location, glob = "*.csv")
sfs_dir_ls(network_location, glob = "*.csv")
```

`sfs_dir_info()`'s columns are a narrower set than `fs::dir_info()`'s --
see `?sfs_dir_info` for which ones and why.

```{r}
staged <- sfs_dir_info(network_location, glob = "*.csv") |>
  sfs_stage_local()
staged

lapply(staged$local_path, read.csv)

sfs_stage_cleanup(staged)
unlink(network_location, recursive = TRUE)
```
